A survey of HTTP caching options on the open Web

### 2015-01-09 sanity/paper1.tex
Future work on collections
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@952 43ef1190-90fd-4dd7-a769-d0121f02b80e
mention qqplot
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@953 43ef1190-90fd-4dd7-a769-d0121f02b80e

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL Endpoints, ontologies, or other information resources,
by a spider detailed in Appendix~\ref{app:fetcher}

@@

We next examine the freshness lifetime of the 2965 information
resources that returned a successful response, either with SPARQL
results or RDF data.

@@

>>>>

The end result of this process is a list of 3117 unique hosts, for
each several resources would be visited, some several times, as they
may host SPARQL Endpoints, ontologies, or other information resources,
by a spider detailed in Appendix~\ref{app:fetcher}, resulting in 7745
requests.

@@

We obtained a successful response from a total 2965 information
resources, either with SPARQL results or RDF data. A successful
response is rather tightly defined, not only must there be a
successful HTTP response after redirects are resolved, the response must also
return a valid RDF media type (unless it is a SPARQL result) and the
RDF must parse into an RDF model.

Since web servers may be configured to instruct clients and proxies to
cache errors differently from successfully served requests, we should
first investigate whether we can simply use all cache headers in the
analysis, or if we should remove unsuccessful responses to avoid
introducing bias to the analysis of valid responses.

For a visual inspection, we may use a quantile-quantile plot to plot
the freshness lifetimes of successful responses versus requests that
failed for some reason. If the distribution of both variables are the
same, these points will draw a straight line. In Figure\todo{include
  qqplot}, we see successful responses vs. the most common parse
error, and it is clear that these are so different that no further
formal analysis is necessary, we must filter unsuccessful requests in
the following analysis.

@@

Investigate whether curated collections such as LOV or SPARQLES
contain resources that has different characteristics. Since the
different sources we surveyed overlap, this cannot be done with
Pearson's $\chi^2$ test, but requires more sophisticated statistics.
